Coronal Fourier power spectra: implications for coronal seismology and coronal heating

### 2014-11-26 tex/paper1/paper1.tex
final edits to the figure

\documentclass[onecolumn]{emulateapj}
%\documentclass[twocolumn]{aastex}
%\documentclass[referee]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
\usepackage{setspace}

@@

\begin{figure}
\epsscale{1.00}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or
  \PL\ \PS\ background on the detection of an oscillatory signal for
  simulated time-series.  Plot (a) shows the simulated time-series,
  generated from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming the null hypothesis that the
  time-series is purely noise, and that the noise has the same average
  power at all wavelet scales.  Plot (c) shows the global wavelet
  \protect\PS\ for this wavelet transform.  Plots (d) and (e) are the
  same as plots (b) and (c) with the null hypothesis that the
  time-series is purely noise, modeled using an auto-regressive AR(1)
  model.  Such time series assume that the current value in a
  time-series depends on its previous value plus some
  Gaussian-distributed noise (\citealp*{chatfieldtimeseries}.)  This
  time-series model gives rise to a \protect\PL\ \protect\PS\ of the
  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
  oscillation, and $n$ is its \PL\ index.  The code used in this
  analysis is an implementation of that described by
  \citet{1998BAMS...79...61T}.}
\label{fig:comparison}
\end{figure}

Figure \ref{fig:comparison} illustrates how a time series generated
from a random sample from a \PL\ \PS\ can be mistakenly thought to
contain a narrow-band oscillatory signal.  The time series in Figure
\ref{fig:comparison}(a) {\BF is a realization of a random process with
  a \PS\ of the form $P(f)\approx f^{-1.77}$ with no explicit
  oscillatory content, using the construction procedure detailed in
  \cite{2010MNRAS.402..307V}.  A different realization of the same
  process with the same \PS\ would almost certainly generate a
  different looking time-series, but since there is more power in
  lower frequencies, lower frequency components are more likely to be
  visible to the eye compared to higher frequency components.}  {\BF
  Figure \ref{fig:comparison}(b) shows that if the null hypothesis is
  that the time-series is purely noise, and that the noise has the
  same average power at all wavelet scales (for example, if the
  time-series were pure Gaussian noise), then the 95\% confidence
  level leads to the positive detection of significant oscillatory
  power in this time series.}  {\BF The detection claim changes if a
  different null hypothesis is used. Figure \ref{fig:comparison}(d) is
  the same as Figure \ref{fig:comparison}(b) except with the null
  hypothesis that the time-series gives rise to a \PL\ \PS\ of the
  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
  oscillation, and $n$ is its \PL\ index}\footnote{{\BF The model
    used to generate a \PL\ \PS\ is an auto-regressive AR(1) model.
    Such time-series assume that the current value in a time-series
    depends on its previous value plus some Gaussian-distributed noise
    \citep{chatfieldtimeseries}.  The null hypothesis that generates
    the \PL\ \PS\ is not important in order to illustrate its effect
    on the detection claim.}}.  This null hypothesis assumption, with
the same confidence level, significantly reduces the area in the
wavelet transform for which a detection may be claimed.  Even with
this significantly different background assumption, there is still a
significant amount of wavelet power above the 95\% confidence level.
However, since the data is simulated without an explicit oscillatory
component, the high wavelet power must have arisen by chance.  The
simulated data, along with the results of Section \ref{sec:anal},
suggest that when examining the wavelet transforms of time-series for
wave packets, a background \PL\ \PS\ should be assumed, along with
higher confidence levels (99\% or higher), in order to minimize the
effects of mistakenly identifying random variations in the background
\PS\ as evidence for an oscillatory signal.  {\BF Since there is a
  \PL\ \PS\ in time-series of coronal emission, evidence for the
  existence of a process that generates narrow-band oscillatory power
  has to {\BF be} measured by its power over and above that expected by the
  \PL\ \PS.}

>>>>

\documentclass[twocolumn]{emulateapj}
%\documentclass[twocolumn]{aastex}
%\documentclass[referee]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
\usepackage{setspace}

@@

\begin{figure}
\epsscale{1.00}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or power-law power
spectrum null hypothesis on the detection of an oscillatory signal for
simulated time series.  Panel (a) shows the simulated time series,
generated from a power spectrum $P(\nu)\propto \nu^{-1.77}$ and with
no explicit oscillation included. Panel (b) shows the normalized
wavelet power spectrum with the cone of influence (shaded/hatched
area) and regions above the 95\% confidence level (thin solid line).
The wavelet power is normalized by the wavelet power expected by
assuming the null hypothesis that the time series is purely white
noise (and therefore the noise has the same power at all wavelet
scales and times). Panel (c) shows the global wavelet power spectrum
for the results of Panel (b): the solid line indicates the global
wavelet power of the simulated data, and the dashed line indicates the
95\% confidence level expected from the null hypothesis. Panels (d)
and (e) are the same as panels (b) and (c) except now the null
hypothesis is that the time series is purely noise and has a power-law
power spectrum of the form $\nu^{-n}, n>0$.  The value of the
power-law index $n$ is estimated by fitting the model $P(\nu)\propto
\nu^{-n}$ to the power-spectrum that creates the time series shown in
Panel (a).  The fit is done using the approach described by
\cite{2010MNRAS.402..307V} and \cite{inglis}.  The code used to
generate the wavelet power spectra (b)-(e) is an implementation of the
wavelet analysis code described by
\protect\citet{1998BAMS...79...61T}.}
\label{fig:comparison}
\end{figure}

Figure \ref{fig:comparison} illustrates how a time series generated
from a random sample from a \PL\ \PS\ can be mistakenly thought to
contain a narrow-band oscillatory signal.  The time series in Figure
\ref{fig:comparison}(a) {\BF is a realization of a random process with
  a \PS\ of the form $P(f)\approx f^{-1.77}$ with no explicit
  oscillatory content, using the construction procedure detailed in
  \cite{2010MNRAS.402..307V}.  A different realization of the same
  process with the same \PS\ would almost certainly generate a
  different looking time-series, but since there is more power in
  lower frequencies, lower frequency components are more likely to be
  visible to the eye compared to higher frequency components.}  {\BF
  Figure \ref{fig:comparison}(b) shows that if the null hypothesis is
  that the time-series is purely noise, and that the noise has the
  same average power at all wavelet scales (for example, if the
  time-series were pure Gaussian noise), then the 95\% confidence
  level leads to the positive detection of significant oscillatory
  power in this time series.}

The detection claim changes if a different null hypothesis is
used. Figure \ref{fig:comparison}(d) is the same as Figure
\ref{fig:comparison}(b) except that the null hypothesis is that the
time-series has a \PL\ \PS\ of the form $\mbox{power}\propto\nu^{-n}$,
where $\nu$ is the frequency of oscillation, and $n$ is its
\PL\ index.  This null hypothesis assumption, with the same confidence
level, significantly reduces the area in the wavelet transform for
which a detection is claimed. The large confident area between 300 and
700 seconds apparent under the white noise null hypothesis (panel b)
is now signifcantly weaker under the power-law power spectrum null
hypothesis, panel (d), but is still present.  However, since the data
is simulated without an explicit oscillatory component, any high
wavelet power must have arisen by chance.  The simulated data, along
with the results of Section \ref{sec:anal}, suggest that when
examining the wavelet transforms of time-series for wave packets, a
background power-law-like \PS\ should be assumed, along with higher
confidence levels (99\% or higher), in order to minimize the effects
of mistakenly identifying random variations in the background \PS\ as
evidence for an oscillatory signal. Since there is a power-law-like
\PS\ in time-series of coronal emission, evidence for the existence of
a process that generates narrow-band oscillatory power has to be
measured by its power over and above that expected by an appropriate
power-law-like model power spectra, such as those given by Equations
\ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump}.
